---
title: "Homework 6 - Iterating functions on Chicago cold"
author: "Damian Velasco"
date: "4/6/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(lubridate)
```

## Exercises

### Exercise 1
```{r write-convert-temperature}
convert_temperature <- function(temperature_vector){
  
  celcius <- (temperature_vector - 32) * (5/9) 
  kelvin <- celcius + 273.15 
    
  tibble("fahrenheit" = temperature_vector,
         "celcius" = celcius,
         "kelvin" = kelvin) 
  
}
```

```{r import-convert-temprature, eval = F}
source("convert_temperature.R")
```

### Exercise 2

Remove this text, and add your answer for Exercise 2 here.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
