---
title: "Homework 6 - Iterating functions on Chicago cold"
author: "Damian Velasco"
date: "4/6/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(lubridate)
```

## Exercises

### Exercise 1


```{r import-convert-temprature, eval = T}
source("convert_temperature.R")
```

### Exercise 2
```{r sanity-check}
convert_temperature(32)
```

### Exercise 3

```{r, import-data}
the_loop <- read_csv("data/chicago-loop.csv")
oak_park <- read_csv("data/chicago-oak-park.csv")
south_loop <- read_csv("data/chicago-south-loop.csv")
```

```{r glimpse-data}
glimpse(the_loop)
glimpse(oak_park)
glimpse(south_loop)
```
### Exercise 4



### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
