---
title: "Lab 06 - Writing functions`"
author: "Damian Velasco"
date: "4/6/23"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
```

## Exercises

### Exercise 1
```{r Survey-new}
class_survey <- read_csv("data/class-survey.csv")
glimpse(class_survey)

```

There are 21 observations in this data set, theses data types are doubles. 

### Exercise 2
```{r pivot-longer, eval= F}
class_survey_long <- class_survey %>%
  mutate(flights = case_when(
    flights == "once" ~ "1",
    TRUE ~ flights
  ),
  flights = as.numeric(flights)) %>%
  
  pivot_longer(
    names_to = "question",
    values_to = "response",
    cols = 2:6
  )
head(class_survey_long, 10)
```

### Exercise 3

```{r summarize-long-data}
class_survey_long %>%
group_by(question) %>%
summarise(min_survey = min(response, na.rm = T),max_survey = max(response, na.rm = T),median_survey = median(response, na.rm = T),mean_survey = mean(response, na.rm = T))

```

### Exercise 4

```{r define-function-body, eval = F}
min(response, na.rm = T)
max(response, na.rm = T)
median(response, na.rm = T)
mean(response, na.rm = T)
```

### Exercise 5
What each response is needing is a response vector. It is a vector because it is a column.

```{r update-input-name, eval = F}

min(response_vector, na.rm = T)
max(response_vector, na.rm = T)
median(response_vector, na.rm = T)
mean(response_vector, na.rm = T)
```

### Exercise 6

I would think that summarize would not be good to call just because 

### Exercise 7

```{r write-compute-summary-stats, eval = T}
compute_summary_stats <- function(response_vector){
  
  min(response_vector, na.rm = T)
  median(response_vector, na.rm = T)
  mean(response_vector, na.rm = T)
  max(response_vector, na.rm = T)

}
```


### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
